Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-04 neurips-20/cvx-flats.tex
Section 3 pass

\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}), while simultaneously appliing to all of the above settings (our four quadrants).
For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to continuous prediction spaces.
As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.

Since indirect elicitation is implied by both consistency and calibration, it might seem a very weak necessary condition for consistency.
Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
In particular, we will derive bounds that imply those given by the feasible subspace dimension approach (Corollary~\ref{cor:fsd-bound}).

@@

\begin{theorem}\label{thm:consistent-implies-indir-elic}
	\btw{Assume L is minnable}If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{theorem}
\begin{proof}
%  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
	By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
	Observe that we use the fact $\Gamma(p) \neq \emptyset$.
	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take $D$ with full support on some $x \in \X$, and let $D_x = p$.
  Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$; in particular $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
%  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
%  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
	Thus, we observe $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
\end{proof}

>>>>

\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\L}{\mathfrak{L}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Sc}{\mathcal{S}}  % jessie, feel free to redef, just not \S :-)
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

In this section, we show that indirect elicitation is necessary for consistency (Theorem \ref{thm:consistent-implies-indir-elic}) for losses in $\L$, while simultaneously applying to all of the above settings (our four quadrants).
For the case of a given discrete target loss, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to continuous prediction spaces.
As we are also interested in the other two quadrants, when given a target statistic instead of as target loss,
we delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result for all four quadrants.

Since indirect elicitation is implied by both consistency and calibration of a surrogate $L \in \L$, it might seem a very weak necessary condition for consistency.
Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
In particular, we will derive bounds that imply those given by the feasible subspace dimension approach (Corollary~\ref{cor:fsd-bound}).

@@

\begin{theorem}\label{thm:consistent-implies-indir-elic}
	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{theorem}
\begin{proof}
%  \raft{Maybe ref the consistency definition here explicitly, at the top and the end}
	By Lemma~\ref{lem:consistent-loss-implies-prop}, it suffices to show the result for consistency with respect to a property $\gamma$, setting $\gamma := \prop{\ell}$ if $\ell$ is given instead.
	We show the contrapositive; suppose $(L, \psi)$ does not indirectly elicit $\gamma$, meaning we have some $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$, where $\Gamma := \prop{L}$.
	Observe that we use the fact $\Gamma(p) \neq \emptyset$.
	Consider the constant sequence $\{f_m\}$ with $f_m(x) = u$ for all $m,x$, and take $D$ with full support on some $x \in \X$, and let $D_x = p$.
  Since $u \in \Gamma(p)$, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$; in particular $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
%  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) = \propdis(\psi(u), p) \neq 0$, since $\psi(u) \not \in \gamma(p)$.
%  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
	Thus, we observe $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
\end{proof}
